Ethnicity sensitive author disambiguation of semi-labeled corpora of scientific articles

### 2015-08-23 paper.tex
save

\begin{figure}
\centering
\label{fig:rfe}
\includegraphics[scale=0.5]{figures/rfe.pdf}
\caption{\glnote{todo}}
\end{figure}

Using Recursive Feature Elimination \cite{guyon2002gene} combined
with feature importances \citep{louppe2013understanding} extracted from GBRT,
we next evaluate the usefulness of all 15 standard and 7
additional ethnicity features used together for learning the linkage function.

@@

\textit{Semi-supervised clustering.}
% compare agglomerative algorithms
% compare threshold strategies
% compare cold start solutions

>>>>

\begin{figure}
\centering
\caption{Recursive Feature Elimimation analysis. }
\label{fig:rfe}
\includegraphics[scale=0.5]{figures/rfe.pdf}
\end{figure}

Using Recursive Feature Elimination \cite{guyon2002gene}, we next evaluate the
usefulness of all 15 standard and 7 additional ethnicity features for learning
the linkage function. The analysis consists in using the baseline algorithm
first using all 22 features, to determine the least discriminative from feature
importances \citep{louppe2013understanding}, and then re-learn the baseline
using all but that one feature. That process is repeated recursively until
eventually only one feature remains. Results are presented in
Figure~\ref{fig:rfe} for one the three folds, starting from the far right with
the baseline and \textit{Second given name} being the least important feature,
and ending on the left with all features eliminated but \textit{Chinese}. As
the figure illustrates, the most important features are ethnic-based features
(\textit{Chinese}, \textit{Other Asian}, \textit{Black}) along with
\textit{Co-authors}, \textit{Affiliation} and \textit{Full name}. Adding the remaining
other features only brings marginal improvements, with \textit{Journal},
\textit{Abstract}, \textit{Collaborations}, \textit{References} \textit{Given
name initial} and \textit{Second given name} being almost insignificant.
Overall, these results highlight the added value of the proposed ehtnic-based
features. Their duality in modeling both the similarity between author names
and their origins make them very strong predictors for author disambiguation.
The results also corroborates results from \citep{ferreira2010effective}, who
found that the similarity between co-authors was a highly discriminative
feature. It indeed appears in 4th in our ranking and brings very significant
improvements. In case computational complexity is a concern, this analysis also
underline the fact that decent performance can be achieved using only a very
limited set of features, as also observed in
\citep{treeratpituk2009disambiguating} or \citep{levin2012citation}.

@@

\textit{Semi-supervised clustering.} The last part of our experiments concerns
the study of agglomerative clustering and the best way to find a cut-off
threshold to form clusters.

% compare agglomerative algorithms
% compare threshold strategies
% compare cold start solutions
